Joker: A Unified Interaction Model For Web Customization

### 2021-08-05 paper.tex
Put back abstract, remove sigconf template reference and persmissions section and trim user study

\settopmatter{printfolios=true}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
%% \begin{abstract}
%%  
%% \end{abstract}

@@

Each session was 60 minutes long and conducted over a recorded video
conference. We started each session with a description of Joker and
provided a brief tutorial of its main features on a sample website not
used in the tasks. There was no time limit for completing the tasks.
Users were encouraged to speak aloud as they worked.

>>>>

\settopmatter{printfolios=true}
\settopmatter{printacmref=false}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
 \begin{abstract}
  Tools that enable end-users to customize websites typically use a
  two-stage workflow: first, users extract data into a structured form;
  second, they use that extracted data to augment the original website
  in some way. This two-stage workflow poses a usability barrier because
  it requires users to make upfront decisions about what data to
  extract, rather than allowing them to incrementally extract data as
  they augment it.

  In this paper, we present a new, unified interaction model for web
  customization that encompasses both extraction and augmentation. The
  key idea is to provide users with a spreadsheet-like formula language
  that can be used for both data extraction and augmentation. We also
  provide a programming-by-demonstration (PBD) interface that allows
  users to create data extraction formulas by clicking on elements in
  the website. This model allows users to naturally and iteratively move
  between extraction and augmentation.

  To illustrate our unified interaction model, we have implemented a
  tool called Joker which is an extension of Wildcard, a prior web
  customization system. Through case studies, we show that Joker can be
  used to customize many real-world websites. We also present a
  formative user study with five participants, which showed that people
  with a wide range of technical backgrounds can use Joker to customize
  websites, and also revealed some interesting limitations of our
  approach. Finally, we present a heuristic evaluation of our design
  using the Cognitive Dimensions framework.
 \end{abstract}

@@
